Parsing Postfix log files

### 2008-04-08 doc/logparser.tex
Added a graph showing the number of mails accepted per day, a table with standard deviation of all days, week days and weekend days, and references to them.

XXX HOW MANY MAILS PER DAY\@?

Section~\ref{parsing coverage} analyses the coverage the parser achieves
over a set of \numberOFlogFILES{} log files taken from a mail server
handling mail for over 700 users.  Coverage is described both in terms of
the fraction of log lines parsed and the fraction of mails and connections
successfully reconstructed by the parsing algorithm, including dealing with
false negatives and a discussion of the difficulties in identifying false
positives.  A random sampling of log lines was parsed, and the correctness
of the results manually verified, as part of determining the coverage of
the parser.

@@

Graphs are an excellent means of displaying data, transforming a
meaningless stream of numbers into an easily comprehensible form, where
anomalies and patterns are immediately obvious.  These graphs are used to
illustrate the topics discussed in \sectionref{rule efficiency}.  The
graphs in the first section cover parser scalability, demonstrating that
performance scales linearly with input size.  The impact of rule ordering
is shown in \sectionref{rule ordering graphs}, and the anomalous dips and
peaks apparent in some graphs are explained.  The third group of graphs
vividly shows the huge impact that caching compiled \regexes{} has on
parser performance.  This section concludes with a breakdown of the rule
hits accumulated during a single test run of the parser.

@@

@@

The graphs presented in this section illustrate the topics discussed in
\sectionref{rule efficiency}.  The first collection of graphs are about
parser scalability, showing the linear relationship between execution time
and input size.  \sectionref{rule ordering graphs} relates to the effect of
rule ordering on execution time, and the unexpected consequences of
specific inputs.  The necessity of caching compiled \regexes{} is attested
to by the third group of graphs, where the difference between caching and
discarding is staggering.  This section concluded with a breakdown of the
rule hits accumulated during a single test run of the parser.

>>>>

Section~\ref{parsing coverage} analyses the coverage the parser achieves
over a set of \numberOFlogFILES{} log files taken from a mail server
handling mail for over 700 users, averaging 8500 mails per day
(graph~\refwithpage{Mails received per day}).  Coverage is described both
in terms of the fraction of log lines parsed and the fraction of mails and
connections successfully reconstructed by the parsing algorithm, including
dealing with false negatives and a discussion of the difficulties in
identifying false positives.  A random sampling of log lines was parsed,
and the correctness of the results manually verified, as part of
determining the coverage of the parser.

@@

Graphs are an excellent means of displaying data, transforming a
meaningless stream of numbers into an easily comprehensible form, where
anomalies and patterns are immediately obvious.  These graphs are used to
illustrate the topics discussed in \sectionref{rule efficiency}.  The
graphs in the first section cover parser scalability, demonstrating that
performance scales linearly with input size.  The impact of rule ordering
is shown in \sectionref{rule ordering graphs}, and the anomalous dips and
peaks apparent in some graphs are explained.  The third group of graphs
vividly shows the huge impact that caching compiled \regexes{} has on
parser performance.  Miscellaneous graphs are presented in the final group
of graphs; these graphs are referenced from various places in the test.
This section concludes with a breakdown of the rule hits accumulated during
a single test run of the parser.

@@

\subsection{Miscellaneous graphs}

\label{Miscellaneous graphs}

\showgraph{build/plot-mails-received}{Mails received per day}{Mails
received per day}

As expected there are far more mails received on weekdays than at weekends.
Note that this graph and the table below show the number of mails received
by \SMTP{} only; in particular the mail loops noticeable in other graphs
do not contribute to these figures.

\showtable{build/mails-received-include-for-graph}{Number of mails received
per day: statistics}{Number of mails received per day: statistics}

@@

The graphs presented in this section illustrate the topics discussed in
\sectionref{rule efficiency}.  The first collection of graphs are about
parser scalability, showing the linear relationship between execution time
and input size.  \sectionref{rule ordering graphs} demonstrates the effect
of rule ordering on execution time, and the unexpected consequences of
specific inputs.  The necessity of caching compiled \regexes{} is attested
to by the third group of graphs, where the difference between caching and
discarding is staggering.  The penultimate section contains a breakdown of
the rule hits accumulated during a single test run of the parser.
Miscellaneous graphs expected to be useful are collected in the final
section.
